Verifying Demonstrations

### 2018-03-21 paper/TimeStamp.tex

With these building blocks we can ensure that a message \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
After time \(t_0\), request \(\rho_{t_0}\gets \TSget\).
Before time \(t_1\), submit \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).

Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land \TStime[\pi_{t_1}] = t_1\).

>>>>

With these building blocks we can ensure that a message \(m\) was created within 
the time interval \(\intrvl{t_0}{t_1}\).
After time \(t_0\), request \(\rho_{t_0}\gets \TSget\).
Before time \(t_1\), submit \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).

Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created 
within the time interval \(\intrvl{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land \TStime[\pi_{t_1}] = t_1\).
